FinalManuscript_DISCS_UG

### 2018-06-24 parts/01_introduction_05scopeandlimitations.tex
did roughly half of methodology

\subsection{Scope of Testing}
We will implement and test the following algorithms:
\begin{enumerate}
	\item A modified version of the Paillier cryptosystem \cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}.
	\item An elliptic curve and ElGamal based cryptosystem for homomorphic encryption presented by Li, et. al. \cite{li_elliptic_2012}.
	\item A fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}, which is an improvement on the original lattice-based cryptosystem presented by Gentry \cite{gentry_fully_2009}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Image adjustment
	\item Operations based on convolution
	\item Morphological operations
\end{enumerate}
We will adopt the benchmark for evaluating the performance and security of image encryption schemes presented by Ahmed, et. al \cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature \cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	\item Tests for preservation of image quality after encryption and decryption.
	\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
		\item Noise tolerance
	\end{enumerate}
	\item Tests for cryptographic security
	\begin{enumerate}
		\item Information entropy analysis
		\item Correlation coefficient analysis
		\item Differential analysis (number of pixel change rate (NPCR), universeral average change intensity (UACI))
	\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the review of related literature.

Images used for testing will be obtained from a database maintained by Gonzalez, et. al. \cite{gonzalez_image_nodate}. Both greyscale and color images will be used.

\subsection{Scope of Implementation}
Our library for OpenCV will be implemented in the C++ programming language.

>>>>

We will implement and test the following algorithms:
\begin{enumerate}
	\item A modified version of the Paillier cryptosystem \cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}.
	\item An elliptic curve and ElGamal based cryptosystem for homomorphic encryption presented by Li, et. al. \cite{li_elliptic_2012}.
	\item A fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}, which is an improvement on the original lattice-based cryptosystem presented by Gentry \cite{gentry_fully_2009}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Image adjustment
	\item Operations based on convolution
	\item Morphological operations
\end{enumerate}
We will adopt the benchmark for evaluating the performance and security of image encryption schemes presented by Ahmed, et. al \cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature \cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	\item Tests for preservation of image quality after encryption and decryption.
	\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
		\item Noise tolerance
	\end{enumerate}
	\item Tests for cryptographic security
	\begin{enumerate}
		\item Information entropy analysis
		\item Correlation coefficient analysis
		\item Differential analysis (number of pixel change rate (NPCR), universeral average change intensity (UACI))
	\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology.
Both greyscale and color images will be used in the study.

Our library for OpenCV will be implemented in the C++ programming language.

The study will only consider the operation of the stated algorithms in a single computer. Client-server models for secure data storage and operation will not be considered.

### 2018-06-24 parts/03_methodology.tex
did roughly half of methodology

After introducing your topic of choice, discussing and relating previous work with your own, and presenting the underlying concepts that your study will be working with, this section will enable you to go into fine detail into how you will go about your study. Essentially, whatever data you need to gather, as well as how you will intend to gather them, should be presented here.
In order to check whether or not your methodology is sound, two main questions should be answered:
\begin{enumerate}
	\item Is your methodology replicable?
	\item Is your methodology realistic and time-bound?
\end{enumerate}

\section{Methodology as Replicable}
A replicable methodology basically means that anyone who reads your methodology and intends to recreate your study to the letter must be able to obtain a similar, if not, exactly the same set of results. It is important, therefore, that you be as specific as you can when describing your methods, such as properly delineating your study’s independent, dependent, and control variables. Much like in the literature review and framework, it is good practice to organize your methodology into subsections for easier readability. Of course, apart from generating data given these variables, included in making the methodology replicable is providing the users an effective and appropriate means to collect data for analysis later on. This assumes, of course, that the data you intend to collect is actually measurable, whether it be quantitative (numerical) or qualitative (descriptive).

\section{Methodology as Realistic and Time-Bound}
On the other hand, a realistic and time-bound methodology takes into consideration the context of the researcher. Although a high-level of competency is expected from a graduating CS major, one must also ensure that the proposed study’s level of difficulty is aligned with what limited resources is available, especially time. In fact, given that the trend is that you will undergo actual implementation only after being able to defend your proposal during the first semester, the study should be accomplishable at the most within only a semester. It is therefore imperative in the methodology, especially in its initial presentation during the defense, that the timetable for the study is thoroughly laid out, with workable time frames and specific dates for deliverables.

\section{Summary and Additional Guide Questions}
The methodology, in summary, is your detailed explanation of how you intend to go about implementing your study.

>>>>

The study consists of two parts: first, the implementation of the three homomorphic encryption schemes and image processing operations under each scheme as an OpenCV library. The second part of the study consists of assessing the robustness and security of image operations under each encryption scheme using benchmarks in \cite{ahmed_benchmark_2016}.

\section{Implementation of the OpenCV library}

The current version of the OpenCV library (3.4.1) will be forked from the open-source GitHub repository at https://github.com/opencv \cite{opencv_library}.

Three homomorphic encryption schemes will be implemented, those presented by Ziad, et al. \cite{ziad_cryptoimg:_2016}, Li, et al. \cite{li_elliptic_2012} and Smart and Vercauteren \cite{hutchison_fully_2010}. The encryption and decryption methods will be implemented in C++.

Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for the following image processing functions, as they are defined in \cite{gonzalez_digital_2008}. We let $R(x,y)$ denote the intensity at coordinate $(x,y)$ in the source image, and $S(x,y)$ denote the intensity at coordinate $(x,y)$ in the resulting image. We further suppose that the intensity values of pixels are in the range $[0, L-1]$.
\begin{description}
	\item[Intensity transformations.] Transformations on the intensities of each of the pixels on an image. The following definitions hold for all $x,y$.
	\begin{enumerate}
		\item Image negation: $S(x,y) = L - 1 - R(x,y)$.
		\item Log transformation: $S(x,y) = c\log{1 + R(x,y)}$, $c \geq 0$.
		\item Power-law transformation: $S(x,y) = c[R(x,y)]^\gamma$, $c > 0, \gamma > 0$.
	\end{enumerate}
	\item[Spatial filters.] Filters implemented by performing a convolution between an $M\times N$ source image and an $m\times n$ filter matrix. Let $W$ be a filter matrix. Then the corresponding spatial filter is given by
	\begin{equation}
		S(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{W(s,t)R(x+s,y+t)}}
	\end{equation}
	\item [Histogram processing / equalization]

\end{description}

\section{Assessment of each homomorphic encryption scheme}

We will first obtain standard test images from \cite{gonzalez_image_nodate}. Both greyscale and color images will be used.

For each image, we will consider each image operation listed above and generate two images: a plaintext domain transformation (PDT) and an encrypted domain transformation (EDT). The PDT will be generated by running the image operation on the

The benchmarks to be used in the study, adopted from \cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below. We let $X_i$ denote from
\begin{enumerate}
	\item Tests for preservation of image quality after encryption and decryption.
	\begin{enumerate}
		\item Mean Squared Error (MSE)

		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
		\item Noise tolerance
	\end{enumerate}
	\item Tests for cryptographic security
	\begin{enumerate}
		\item Information entropy analysis
		\item Correlation coefficient analysis
		\item Differential analysis (number of pixel change rate (NPCR), universeral average change intensity (UACI))
	\end{enumerate}
\end{enumerate}
